Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-11-18 paper.tex
Addressing z_init and fragmentation points

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  \textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.}

@@

If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. \textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. We found that even when this number was decreased to 0.065 pc, the number of stars which formed was unchanged.} The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above. \textbf{The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$. }Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses $<1 M_{\odot}$. The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars, similar to the radiation hydrodynamic simulations of \citet{Susa13, Susa14}. It should be noted that these halos are not necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it did not host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$. Note that the mass of the Pop III stars depends on the chosen IMF.

>>>>

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc.  \textbf{We refine the cells when one of the following criteria are met: (1) the baryon or dark matter overdensity exceeds $3\bar{\rho}_{\rm b,DM} \times 2^{\ell(3+\epsilon)}$, or (2) the local Jeans length is less than eight cell widths.  Here $\rho_{\rm b,DM}$ is the baryon or dark matter cosmic mean density, $\ell$ is the AMR level, and $\epsilon = -0.2$ invokes super-Lagrangian refinement behavior.} The simulation is initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit \citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables having their usual definitions. \textbf{We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.} The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units, unless otherwise specified.}

@@

If within \textbf{10} pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. \textbf{In a parameter study, we have found that the number of Pop III star particles is insensitive to this algorithmic merging distance. We found that even when this number was decreased to 0.065 pc, the number of star particles that formed was unchanged.  Our density threshold for star particle formation is equivalent to a molecular core.  Fragmentation of metal-free gas into massive stellar precursors can occur at scales down to 1000~AU \citep[e.g.][]{Turk09, Stacy11} with molecular cores, therefore our results on multiplicity should be considered as lower limits.}

The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above. \textbf{The Pop III IMF mass ranges from $1 \leq M / M_{\odot} \leq 300$. }Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. \textbf{Again, we are only tracking the formation of metal-free molecular cores, which form either a single or multiple massive Pop III stars and perhaps several more low mass stars.}

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking \textbf{star-forming regions where the star particles form at densities equivalent to molecular cores that may form multiple massive stars.  Furthermore, we are not modeling the formation of low-mass stars ($<1 M_{\odot}$) that may form out of fragmented gas at higher densities and smaller scales.  Thus our results in this section should be considered as lower limits to the number of Pop III stars.}  The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars, similar to the radiation hydrodynamic simulations of \citet{Susa13, Susa14}. It should be noted that these halos are not necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it did not host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$. Note that the mass of the Pop III stars depends on the chosen IMF.

### 2019-11-18 referee_2.tex
Minor changes to make Second response compilable
Addressing z_init and fragmentation points

@@

\begin{referee}
    D -- - The initialization at z=130 should be mentioned as a caveat. 
\end{referee}

@@

\begin{referee}
    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea & Normal 07 paper that was performed. 
\end{referee}
    The citation previously written was referencing their first paper in their series of Pop III star formation. It should have referenced their second paper in the series. This has been corrected.

    O'Shea and Norman 2008 do not provide an analytic fit for the H2 radial profile. The profile used in our calculations were taken from their figure 13 panel d. This detail has been added in the description of the H2 radial profiles.

\begin{referee}
    E.3 -- -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding. I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding. Maybe it has to do with the scaling of the H2 fraction?  It is important to know how the authors scale the H2 fraction as a function of radius for different halo masses (see point above). If this is not the reason, please explain what else is causing more massive haloes to be worse at self-shielding.  
\end{referee}
    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to smaller radii. So halos with smaller masses, and thus smaller virial radii, have more \hh{} built up at the edges compared to their larger counterparts, resulting in a more effective shield at the virial radius.

@@

>>>>

    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section. I think with these statements, we can argue in the response that changes throughout the text are not needed.}

@@

\begin{referee}
    D -- - The initialization at z=130 should be mentioned as a caveat. 
\end{referee}
We have added the following text to Section 2.1 after stating the initialization redshift, ``We note that this initialization redshift is too low, even with 2nd order Lagrangian perturbation theory, for a small cosmological volume and results in delayed structure formation at very high redshift $z > 20$.''

@@

\begin{referee}
    E.2 -- -- For completeness, please provide the readers with the H2 radial fit to the O'Shea \& Normal 07 paper that was performed. 
\end{referee}
    The citation previously written was referencing their first paper in their series of Pop III star formation. It should have referenced their second paper in the series. This has been corrected.

    O'Shea and Norman 2008 do not provide an analytic fit for the H$_2$ radial profile. The profile used in our calculations were taken from their figure 13 panel d. This detail has been added in the description of the H$_2$ radial profiles.

    \jhw{You should give the exact fitting formula in the text.}

\begin{referee}
    E.3 -- -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding. I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding. Maybe it has to do with the scaling of the H2 fraction?  It is important to know how the authors scale the H2 fraction as a function of radius for different halo masses (see point above). If this is not the reason, please explain what else is causing more massive haloes to be worse at self-shielding.  
\end{referee}
    The shielding factor increases for more massive halos because these halos have larger virial radii, at which point there is significantly less \hh{} compared to smaller radii. So halos with smaller masses, and thus smaller virial radii, have more \hh{} built up at the edges compared to their larger counterparts, resulting in a more effective shield at the virial radius. We have clarified this point in the text.

@@

\end{document}
